### 2021-05-07 manuscript/manuscript.Rmd
add list of studies
add unpublished study

## Transparency

@@

***Study Setting.*** For each sample, we recorded in what country (or countries) the data was collected ($\kappa = .97$) and what the disadvantaged ingroup and the advantaged outgroup were. We categorized each sample’s setting according to whether the source of the groups’ relative inequality was long-term migration (e.g., Asian Americans), short-term  migration (e.g., international students), slavery (e.g., Black Americans), colonization (e.g., Māori, Black South Africans), religion, caste, sexuality, or another distinction ($\kappa = .84$).

@@

***Outcome Variables.*** For each measure of perceived injustice, we coded whether it refered to specific instances of discrimination, to a more general perception of discrimination, or to both ($\kappa = .67$) and whether it assessed personal discrimination, group discrimination, or both ($\kappa = .83$).

@@

```{=latex}
\begin{figure*}
\centering
\caption{Posterior distributions from the random-effects meta-analysis models with alternative predictor variables}
\includegraphics[scale=1]{../figures/figure-8}
\label{fig:f8}
\end{figure*}
```

>>>>

## Open Practices Statement

@@

***Study Setting.*** For each sample, we recorded in what country (or countries) the data was collected ($\kappa = .97$) and what the disadvantaged ingroup and the advantaged outgroup were. We categorized each sample’s setting according to whether the source of the groups’ relative inequality was long-term migration (e.g., Asian Americans), short-term  migration (e.g., international students), slavery (e.g., Black Americans), colonization (e.g., Māori, Black South Africans), religion, caste, sexuality, or another distinction ($\kappa = .85$).

@@

***Outcome Variables.*** For each measure of perceived injustice, we coded whether it refered to specific instances of discrimination, to a more general perception of discrimination, or to both ($\kappa = .67$) and whether it assessed personal discrimination, group discrimination, or both ($\kappa = .84$).

@@

```{=latex}
\begin{figure*}[t!]
\centering
\caption{Posterior distributions from the random-effects meta-analysis models with alternative predictor variables}
\includegraphics[scale=1]{../figures/figure-8}
\label{fig:f8}
\end{figure*}
```

### 2021-05-07 records/list-of-records.tex
add unpublished study

@@

\cite{1494} & 3 & 237 & .02 & Cross-Sectional & Probability & > 18 & N. America & USA & Post-Slavery & No & No\\
 & 4 & 235 & .01 & Cross-Sectional & Probability & > 18 & N. America & USA & L.-T. Migration & No & No\\

@@

\cite{813} & 2 & 175 & -.22 & Cross-Sectional & Students & > 18 & Asia & Israel & Post-Colonial & Yes & Yes\\

@@

\cite{1966} & 1 & 506 & .00 & Cross-Sectional & Convenience & < 18 & Europe & Germany & L.-T. Migration & Yes & No\\
 & 1 & 506 & -.04 & Cross-Sectional & Convenience & < 18 & Europe & Germany & L.-T. Migration & Yes & No\\
 & 2 & 506 & -.07 & Cross-Sectional & Convenience & < 18 & Asia & Israel & L.-T. Migration & Yes & No\\
 & 2 & 506 & -.12 & Cross-Sectional & Convenience & < 18 & Asia & Israel & L.-T. Migration & Yes & No\\

@@

  \cite{3201} & 1 & 159 & -.19 & Cross-Sectional & Convenience & > 18 & Asia & Palestine & Post-Colonial & Yes & Yes\\
\cite{322} & 1 & 151 & -.10 & Cross-Sectional & Students & > 18 & Asia & Turkey & Post-Colonial & Yes & Yes\\
\cite{414} & 1 & 269 & .31 & Cross-Sectional & Convenience & > 18 & Asia & Turkey & Other & Yes & Yes\\
\cite{2075} & 1 & 81 & -.35 & Experimental & Students & > 18 & N. America & Canada & Other & Yes & Yes\\
\cite{2397} & 1 & 501 & .05 & Cross-Sectional & Probability & > 18 & Europe & UK & L.-T. Migration & No & Yes\\
\cite{284} & 1 & 488 & -.29 & Cross-Sectional & Students & > 18 & Africa & S. Africa & Post-Colonial & Yes & Yes\\
\cite{1248} & 1 & 209 & -.13 & Cross-Sectional & Convenience & > 18 & Asia & Turkey & Post-Colonial & Yes & Yes\\
\cite{3196} & 1 & 165 & .20 & Cross-Sectional & Students & < 18 & Europe & Italy & L.-T. Migration & Yes & Yes\\
\cite{93} & 1 & 449 & .15 & Cross-Sectional & Students & > 18 & Asia & India & Religion & Yes & Yes\\
\cite{2033} & 1 & 203 & .05 & Experimental & Students & > 18 & N. America & Canada & L.-T. Migration & Yes & Yes\\
\cite{3054} & 1 & 1,000 & -.04 & Cross-Sectional & Convenience & > 18 & Multiple & Multiple & Multiple & Yes & Yes\\
 & 11 & 3,883 & -.09 & Cross-Sectional & Convenience & > 18 & Multiple & Multiple & Sexuality & Yes & Yes\\
\cite{2309} & 1 & 195 & .08 & Cross-Sectional & Convenience & > 18 & N. America & USA & Post-Slavery & Yes & Yes\\
 & 2 & 170 & -.03 & Cross-Sectional & Convenience & > 18 & N. America & USA & L.-T. Migration & Yes & Yes\\
\cite{894} & 1 & 176 & -.12 & Cross-Sectional & Students & > 18 & N. America & USA & L.-T. Migration & No & Yes\\
 & 2 & 126 & -.10 & Cross-Sectional & Students & > 18 & N. America & USA & Post-Slavery & No & Yes\\
\cite{1376} & 1 & 85 & -.30 & Cross-Sectional & Students & > 18 & Europe & UK & Religion & Yes & Yes\\
\cite{4004} & 1 & 320 & .16 & Cross-Sectional & Convenience & < 18 & Europe & Bulgaria & Other & Yes & Yes\\
\cite{2391} & 1 & 400 & .04 & Longitudinal & Convenience & > 18 & Europe & Italy & L.-T. Migration & No & Yes\\
\cite{956} & 1 & 233 & -.03 & Cross-Sectional & Students & > 18 & Europe & UK & Sexuality & Yes & Yes\\
 & 2 & 433 & .05 & Longitudinal & Students & > 18 & Multiple & Multiple & Sexuality & Yes & Yes\\
\cite{1114} & 1 & 581 & -.28 & Cross-Sectional & Probability & > 18 & Asia & Lebanon & L.-T. Migration & Yes & Yes\\
\cite{2382} & 1 & 751 & -.22 & Longitudinal & Probability & < 18 & Europe & UK & L.-T. Migration & No & Yes\\
\cite{2381} & 1 & 1,977 & -.06 & Longitudinal & Probability & > 18 & Oceania & NZ & Post-Colonial & No & No\\
 & 2 & 526 & .00 & Longitudinal & Probability & > 18 & Oceania & NZ & L.-T. Migration & No & No\\
 & 3 & 684 & .02 & Longitudinal & Probability & > 18 & Oceania & NZ & L.-T. Migration & No & No\\
\cite{2385} & 1 & 4,708 & .03 & Cross-Sectional & Probability & > 18 & Asia & India & Religion & No & Yes\\
\cite{2392} & 1 & 13,646 & -.03 & Cross-Sectional & Probability & > 18 & Asia & India & Caste & No & Yes\\
 & 2 & 1,526 & -.28 & Cross-Sectional & Probability & > 18 & Asia & India & Religion & No & Yes\\
 & 2 & 49,764 & -.02 & Cross-Sectional & Probability & > 18 & Asia & India & Caste & No & Yes\\
 & 3 & 935 & -.02 & Cross-Sectional & Probability & > 18 & Asia & India & Religion & No & Yes\\
 & 3 & 33,137 & -.03 & Cross-Sectional & Probability & > 18 & Asia & India & Caste & No & Yes\\
 & 4 & 271 & .08 & Cross-Sectional & Probability & > 18 & Asia & India & Religion & No & Yes\\
\cite{2375} & 1 & 112 & -.23 & Cross-Sectional & Students & > 18 & N. America & USA & L.-T. Migration & Yes & Yes\\
\cite{1743} & 1 & 72 & -.12 & Longitudinal & Students & > 18 & N. America & USA & Post-Slavery & Yes & Yes\\
 & 2 & 282 & -.17 & Longitudinal & Students & > 18 & N. America & USA & L.-T. Migration & Yes & Yes\\
 & 3 & 417 & .03 & Longitudinal & Students & > 18 & N. America & USA & L.-T. Migration & Yes & Yes\\

@@

 \cite{284} & 1 & 488 & -.27 & Cross-Sectional & Students & > 18 & Africa & S. Africa & Post-Colonial & Yes & Yes\\
\cite{1614} & 1 & 320 & -.23 & Cross-Sectional & Students & > 18 & Asia & Turkey & Post-Colonial & Yes & Yes\\
\cite{3205} & 1 & 602 & -.09 & Cross-Sectional & Probability & > 18 & Europe & Romania & Other & Yes & Yes\\
\cite{1386} & 1 & 1,556 & -.09 & Cross-Sectional & Probability & > 18 & Africa & S. Africa & Post-Colonial & Yes & Yes\\
\cite{1549} & 1 & 658 & -.09 & Cross-Sectional & Probability & > 18 & N. America & USA & Post-Slavery & No & Yes\\
\cite{3054} & 1 & 1,000 & -.01 & Cross-Sectional & Convenience & > 18 & Multiple & Multiple & Multiple & Yes & Yes\\
 & 11 & 3,883 & -.09 & Cross-Sectional & Convenience & > 18 & Multiple & Multiple & Sexuality & Yes & Yes\\
\cite{856} & 1 & 187 & .06 & Cross-Sectional & Students & < 18 & Europe & Macedonia & Other & Yes & Yes\\
\cite{1042} & 1 & 165 & .17 & Cross-Sectional & Students & > 18 & N. America & USA & L.-T. Migration & Yes & Yes\\
 & 2 & 92 & .10 & Cross-Sectional & Students & > 18 & N. America & USA & Post-Slavery & Yes & Yes\\
\cite{2380} & 1 & 76 & -.10 & Cross-Sectional & Students & > 18 & Asia & India & Caste & No & Yes\\
 & 2 & 127 & -.04 & Cross-Sectional & Students & > 18 & Asia & India & Caste & No & Yes\\
\cite{4005} & 1 & 74 & -.24 & Cross-Sectional & Students & > 18 & Asia & Israel & L.-T. Migration & Yes & Yes\\
\cite{813} & 2 & 175 & .00 & Cross-Sectional & Students & > 18 & Asia & Israel & Post-Colonial & Yes & Yes\\
\cite{1695} & 1 & 1,008 & .03 & Cross-Sectional & Probability & > 18 & Oceania & NZ & Post-Colonial & Yes & Yes\\
\cite{2381} & 1 & 1,977 & -.02 & Longitudinal & Probability & > 18 & Oceania & NZ & Post-Colonial & No & No\\
 & 2 & 526 & -.00 & Longitudinal & Probability & > 18 & Oceania & NZ & L.-T. Migration & No & No\\
 & 3 & 684 & -.00 & Longitudinal & Probability & > 18 & Oceania & NZ & L.-T. Migration & No & No\\
\cite{286} & 1 & 105 & -.14 & Cross-Sectional & Convenience & > 18 & Asia & Turkey & Post-Colonial & Yes & Yes\\

>>>>

\cite{2398} & 1 & 829 & -.03 & Longitudinal & Students & < 18 & Europe & UK & L.-T. Migration & No & No\\

@@

\cite{1494} & 1 & 237 & .02 & Cross-Sectional & Probability & > 18 & N. America & USA & Post-Slavery & No & No\\
 & 2 & 235 & .01 & Cross-Sectional & Probability & > 18 & N. America & USA & L.-T. Migration & No & No\\

@@

\cite{813} & 1 & 175 & -.22 & Cross-Sectional & Students & > 18 & Asia & Israel & Post-Colonial & Yes & Yes\\

@@

\cite{1966} & 1 & 506 & -.01 & Cross-Sectional & Convenience & < 18 & Europe & Germany & L.-T. Migration & Yes & No\\
 & 2 & 506 & -.09 & Cross-Sectional & Convenience & < 18 & Asia & Israel & L.-T. Migration & Yes & No\\

@@

\cite{3201} & 1 & 159 & -.19 & Cross-Sectional & Convenience & > 18 & Asia & Palestine & Post-Colonial & Yes & Yes\\
\cite{322} & 1 & 151 & -.10 & Cross-Sectional & Students & > 18 & Asia & Turkey & Post-Colonial & Yes & Yes\\
\cite{414} & 1 & 269 & .31 & Cross-Sectional & Convenience & > 18 & Asia & Turkey & Other & Yes & Yes\\
\cite{2075} & 1 & 81 & -.35 & Experimental & Students & > 18 & N. America & Canada & Other & Yes & Yes\\
\cite{2397} & 1 & 501 & .05 & Cross-Sectional & Probability & > 18 & Europe & UK & L.-T. Migration & No & Yes\\
\cite{284} & 1 & 488 & -.29 & Cross-Sectional & Students & > 18 & Africa & S. Africa & Post-Colonial & Yes & Yes\\
\cite{1248} & 1 & 209 & -.13 & Cross-Sectional & Convenience & > 18 & Asia & Turkey & Post-Colonial & Yes & Yes\\
\cite{3196} & 1 & 165 & .20 & Cross-Sectional & Students & < 18 & Europe & Italy & L.-T. Migration & Yes & Yes\\
\cite{93} & 1 & 449 & .15 & Cross-Sectional & Students & > 18 & Asia & India & Religion & Yes & Yes\\
\cite{2033} & 1 & 203 & .05 & Experimental & Students & > 18 & N. America & Canada & L.-T. Migration & Yes & Yes\\
\cite{3054} & 1 & 1,000 & -.04 & Cross-Sectional & Convenience & > 18 & Multiple & Multiple & Multiple & Yes & Yes\\
 & 2 & 3,883 & -.09 & Cross-Sectional & Convenience & > 18 & Multiple & Multiple & Sexuality & Yes & Yes\\
\cite{2309} & 1 & 195 & .08 & Cross-Sectional & Convenience & > 18 & N. America & USA & Post-Slavery & Yes & Yes\\
 & 2 & 170 & -.03 & Cross-Sectional & Convenience & > 18 & N. America & USA & L.-T. Migration & Yes & Yes\\
\cite{894} & 1 & 176 & -.12 & Cross-Sectional & Students & > 18 & N. America & USA & L.-T. Migration & No & Yes\\
 & 2 & 126 & -.10 & Cross-Sectional & Students & > 18 & N. America & USA & Post-Slavery & No & Yes\\
\cite{1376} & 1 & 85 & -.30 & Cross-Sectional & Students & > 18 & Europe & UK & Religion & Yes & Yes\\
\cite{4004} & 1 & 320 & .16 & Cross-Sectional & Convenience & < 18 & Europe & Bulgaria & Other & Yes & Yes\\
\cite{2391} & 1 & 400 & .04 & Longitudinal & Convenience & > 18 & Europe & Italy & L.-T. Migration & No & Yes\\
\cite{956} & 1 & 233 & -.03 & Cross-Sectional & Students & > 18 & Europe & UK & Sexuality & Yes & Yes\\
 & 2 & 433 & .05 & Longitudinal & Students & > 18 & Multiple & Multiple & Sexuality & Yes & Yes\\
\cite{1114} & 1 & 581 & -.28 & Cross-Sectional & Probability & > 18 & Asia & Lebanon & L.-T. Migration & Yes & Yes\\
\cite{2382} & 1 & 751 & -.22 & Longitudinal & Probability & < 18 & Europe & UK & L.-T. Migration & No & Yes\\
\cite{2381} & 1 & 1,977 & -.06 & Longitudinal & Probability & > 18 & Oceania & NZ & Post-Colonial & No & No\\
 & 2 & 526 & .00 & Longitudinal & Probability & > 18 & Oceania & NZ & L.-T. Migration & No & No\\
 & 3 & 684 & .02 & Longitudinal & Probability & > 18 & Oceania & NZ & L.-T. Migration & No & No\\
\cite{2385} & 1 & 4,708 & .03 & Cross-Sectional & Probability & > 18 & Asia & India & Religion & No & Yes\\
 & 2 & 1,526 & -.28 & Cross-Sectional & Probability & > 18 & Asia & India & Religion & No & Yes\\
 & 3 & 935 & -.02 & Cross-Sectional & Probability & > 18 & Asia & India & Religion & No & Yes\\
 & 4 & 271 & .08 & Cross-Sectional & Probability & > 18 & Asia & India & Religion & No & Yes\\
\cite{2392} & 1 & 13,646 & -.03 & Cross-Sectional & Probability & > 18 & Asia & India & Caste & No & Yes\\
 & 2 & 49,764 & -.02 & Cross-Sectional & Probability & > 18 & Asia & India & Caste & No & Yes\\
 & 3 & 33,137 & -.03 & Cross-Sectional & Probability & > 18 & Asia & India & Caste & No & Yes\\
\cite{2375} & 1 & 112 & -.23 & Cross-Sectional & Students & > 18 & N. America & USA & L.-T. Migration & Yes & Yes\\
\cite{1743} & 1 & 72 & -.12 & Longitudinal & Students & > 18 & N. America & USA & Post-Slavery & Yes & Yes\\
 & 2 & 282 & -.17 & Longitudinal & Students & > 18 & N. America & USA & L.-T. Migration & Yes & Yes\\
 & 3 & 417 & .03 & Longitudinal & Students & > 18 & N. America & USA & L.-T. Migration & Yes & Yes\\

@@

\cite{284} & 1 & 488 & -.27 & Cross-Sectional & Students & > 18 & Africa & S. Africa & Post-Colonial & Yes & Yes\\
\cite{1614} & 1 & 320 & -.23 & Cross-Sectional & Students & > 18 & Asia & Turkey & Post-Colonial & Yes & Yes\\
\cite{3205} & 1 & 602 & -.09 & Cross-Sectional & Probability & > 18 & Europe & Romania & Other & Yes & Yes\\
\cite{1386} & 1 & 1,556 & -.09 & Cross-Sectional & Probability & > 18 & Africa & S. Africa & Post-Colonial & Yes & Yes\\
\cite{1549} & 1 & 658 & -.09 & Cross-Sectional & Probability & > 18 & N. America & USA & Post-Slavery & No & Yes\\
\cite{3054} & 1 & 1,000 & -.01 & Cross-Sectional & Convenience & > 18 & Multiple & Multiple & Multiple & Yes & Yes\\
 & 2 & 3,883 & -.09 & Cross-Sectional & Convenience & > 18 & Multiple & Multiple & Sexuality & Yes & Yes\\
\cite{856} & 1 & 187 & .06 & Cross-Sectional & Students & < 18 & Europe & Macedonia & Other & Yes & Yes\\
\cite{1042} & 1 & 165 & .17 & Cross-Sectional & Students & > 18 & N. America & USA & L.-T. Migration & Yes & Yes\\
 & 2 & 92 & .10 & Cross-Sectional & Students & > 18 & N. America & USA & Post-Slavery & Yes & Yes\\
\cite{2380} & 1 & 76 & -.10 & Cross-Sectional & Students & > 18 & Asia & India & Caste & No & Yes\\
 & 2 & 127 & -.04 & Cross-Sectional & Students & > 18 & Asia & India & Caste & No & Yes\\
\cite{4005} & 1 & 74 & -.24 & Cross-Sectional & Students & > 18 & Asia & Israel & L.-T. Migration & Yes & Yes\\
\cite{813} & 1 & 175 & .00 & Cross-Sectional & Students & > 18 & Asia & Israel & Post-Colonial & Yes & Yes\\
\cite{1695} & 1 & 1,008 & .03 & Cross-Sectional & Probability & > 18 & Oceania & NZ & Post-Colonial & Yes & Yes\\
\cite{2381} & 1 & 1,977 & -.02 & Longitudinal & Probability & > 18 & Oceania & NZ & Post-Colonial & No & No\\
 & 2 & 526 & -.00 & Longitudinal & Probability & > 18 & Oceania & NZ & L.-T. Migration & No & No\\
 & 3 & 684 & -.00 & Longitudinal & Probability & > 18 & Oceania & NZ & L.-T. Migration & No & No\\
\cite{286} & 1 & 105 & -.14 & Cross-Sectional & Convenience & > 18 & Asia & Turkey & Post-Colonial & Yes & Yes\\
